---
title: "Govhack 2017"
output: html_notebook
---

Download libraries.
```{r}
library(ggplot2)
```

Dataframe for the weights, scenario and age mapping.
```{r}
master_table <- master_tabler_new

zombie_attack_weights = c(-5,0,-1,1,0,0)
fire_outbreak_weights = c(-0.5,0,0,1.5,0,5)
earthquake_weights = c(0,-5,0.5,-2,3,0)

df = data.frame(zombie_attack_weights,fire_outbreak_weights,earthquake_weights)  
```

Function calculate survival index
```{r}
calculate_survival <- function(scenario, age, table){
  
  Age_Norm <- 0.5
  if (age < 12) { Age_Norm <- 0.1}
  else if (age < 20) { Age_Norm <- 0.2}
  else if (age < 35) { Age_Norm <- 0.3}
  else if (age < 49) { Age_Norm <- 0.4}
  else if (age < 60) { Age_Norm <- 0.5}
  else if (age < 70) { Age_Norm <- 0.6}
  else if (age < 90) { Age_Norm <- 0.7}
  else Age_Norm <- 0.8
  
  if (scenario=='Zombie Attack') {
    weights <- zombie_attack_weights
  } else if (scenario=='Fire Outbreak') {
    weights <- fire_outbreak_weights
  } else weights <- earthquake_weights
  
  my_table <- table
  
  survival_index_suburb <- weights[1] * my_table$Density_Norm + weights[2] * my_table$Income_Norm + weights[3] * my_table$Earthquake_Norm + weights[4] * my_table$Hospital_Norm + weights[5] * Age_Norm + weights[6] * my_table$Water_Norm
  
  survival_index_suburb <- (survival_index_suburb+1)*50
  
  return(survival_index_suburb)
  
}
```

subset abs_pop_age and merge
```{r}
abs_pop_age$Code <- abs_pop_age$ASGS_2016
abs_pop_age_subset <- abs_pop_age[which(abs_pop_age$SEX_ABS == 3 & abs_pop_age$REGIONTYPE == "SA2" & abs_pop_age$Age != "All ages"),]
abs_pop_age_subset$Age <- as.integer(abs_pop_age_subset$Age)

is.integer(abs_pop_age_subset$Age)

all <- merge(x = abs_pop_age_subset, y = master_table, by = "Code", all.x = TRUE)

```
need to apply function to all age groups
sapply(all, function(x) calculate_survival('Zombie Attack',x[3],all))


Map population vs survival index

Map yourself against population

```{r}
my_location_code <- 10042
my_age <- 90
my_scenario <- 'Fire Outbreak'

master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)

 ggplot(data = master_table , aes(x = calculate_survival(my_scenario,my_age,master_table), y = Population)) + 
  geom_point() + 
  geom_point(data = master_table[which(master_table$Code==my_location_code),], aes (x = survival_index, y = Population), colour = 'red') +
  ggtitle("Fire Outbreak Survival Index") +
  labs(y= "Population", x = "Survival Index")
```

1. Fire Outbreak Population Map
```{r}
my_age <- 40
my_scenario <- 'Fire Outbreak'

master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)

ggplot(data = master_table , aes(x = calculate_survival(my_scenario,my_age,master_table), y = Population)) + 
  geom_point() + 
  ggtitle("Fire Outbreak Survival Index") +
  labs(y= "Population", x = "Survival Index")
```


2. Zombie Attack Population Map
```{r}
my_age <- 40
my_scenario <- 'Zombie Attack'

master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)

ggplot(data = master_table , aes(x = calculate_survival(my_scenario,my_age,master_table), y = Population)) + 
  geom_point() + 
  ggtitle("Zombie Attack Survival Index") +
  labs(y= "Population", x = "Survival Index")
```


3. Earthquake Population Map
```{r}
my_age <- 40
my_scenario <- 'Earthquake'

master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)

ggplot(data = master_table , aes(x = calculate_survival(my_scenario,my_age,master_table), y = Population)) + 
  geom_point() + 
  ggtitle("Earthquake Survival Index") +
  labs(y= "Population", x = "Survival Index")
```


Find min and max suburbs functions
```{r}
find_worse_suburb <- function(my_scenario,my_age,master_table) {
  master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)
  master_table[which.min(master_table$survival_index),]$Suburb
}

find_best_suburb <- function(my_scenario,my_age,master_table) {
  master_table$survival_index <- calculate_survival(my_scenario,my_age,master_table)
  master_table[which(master_table$survival_index == max(master_table$survival_index)),]$Suburb
}
```


Zombie Attack
```{r}
find_worse_suburb('Zombie Attack',40,master_table)
find_best_suburb('Zombie Attack',40,master_table)

min(master_table$survival_index,na.rm = TRUE)
```

Fire
```{r}
find_worse_suburb('Fire Outbreak',40,master_table)
find_best_suburb('Fire Outbreak',40,master_table)
```

Earthquake
```{r}
find_worse_suburb('Earthquake',40,master_table)
find_best_suburb('Earthquake',40,master_table)
```